---
title: Hospital-Acquired SARS-CoV-2
subtitle: Exact Match, Followed by Propensity Score Matching Analysis, Relative Risk Outcomes
author: 
date: 
output:
  word_document:
    reference_docx: word_styles.docx
    df_print: kable
  html_document: default
  pdf_document: default
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_file = 'ho_COVID_vax_status_RR_2024-05-22.docx',
      envir = globalenv()
    )
  })
---

```{r,include=FALSE}
library(tidyverse)
library(survival)
library(ipw)
library(optmatch)
library(lubridate)
library(MatchIt)
library(naniar)
library(lmtest)
library(RItools)
library(sandwich)
library(broom)
library(knitr)
library(cobalt)

filesfx <- "vax_status_2024-05-08"
outfilesfx <- "vax_status_RR_2024-05-22"

loc <- "/data/tide/projects/ho-covid/annals_resubmission/add_addtl_vars_dr5_sdm/sensitivity_analyses/vax_status"

dataLoc <- paste0(loc,"/data")
outLoc <- paste0(loc,"/output")


# setwd("/external/BWH-ICRESEARCH/Projects/Hospital Onset COVID")
covid_data_simulation <- readRDS(file.path(dataLoc,paste0("covid_data_simulation_",filesfx,".Rds")))

matchedF <- paste0("covid_data_simulation_matched_",filesfx,".Rds")

new_events <- readRDS(file.path(dataLoc,"ho_covid_after_match_new_events_vax_status_2024-05-22.Rds"))
```
  
## Inclusion Criteria
Patients were included in analysis if they met **all** of the following criteria:
  
- Admission to BWH, MGH, BWF, NSMC, NWH on or after December 1, 2020 through April 30, 2023
- Age >= 18
- Hospital length of stay >= 5 days

## Exclusions
Patients were excluded from analysis if they met **any** of the following criteria:
  
- COVID flag active on hospital day 1 - 4


## Case Definition
Cases were defined as:
  
- Activation of COVID-19 flag on hospital day 5 or greater
- COVID-19 flag remains active for >= 4 days (including post-discharge)


## Study Population
```{r}
# N Hospitalizations
nrow(distinct(covid_data_simulation,hospID))

# Min Admit Date
min(covid_data_simulation$admitDT)

# Max Admit Date
max(covid_data_simulation$admitDT)

# N Hospital Days
nrow(covid_data_simulation)

# N Cases
nrow(covid_data_simulation %>% filter(case==1))
```


## Matching
Cases are matched to controls in three steps.

1. Exact match on:

- Hospital
- Service group on match day minus 2
- ICU status on match day minus 2

2. Caliper match on:
- LOS for controls greater than or equal to match day for case
- Admit date within 90 days
- Propensity score standardized difference  < 0.2


```{r}
covid_data_simulation_matched <- readRDS(file.path(dataLoc,matchedF)) %>% 
   mutate(ttmatch_days= as.numeric((date-admitDT)+1),
         matchtodischarge_days= as.numeric(dischargeDT-date))

# N matches
nrow(distinct(covid_data_simulation_matched,matchid))
```

## Balance Results Using Cobalt 
### Pre-Omicron
```{r}
pre_omicron <- covid_data_simulation_matched %>% filter(cov_grp==0)

covs <- pre_omicron %>% 
  select(encAge,gender,raceEthnicity,dischargeLocation2,encDeathDerived,
         dischargeDispositionGroup2,prevDischarge90Days,LOS,facility_admission,
         starts_with("elix_"),
         maxTemp,medRR,medSBP,medDBP,maxALT,maxTBILI,minALB,minSODIUM,maxCREAT,
         minPLT,maxWBC,minHCT,maxGLU,ICUalgo,serviceGroup2,ttmatch_days,matchtodischarge_days,
         covVaxEver,covVaxLast4months,covVaxCumSum)

bal.tab(case ~ covs, data = pre_omicron, binary = "std", continuous = "std")
```

### Omicron
```{r}
post_omicron <- covid_data_simulation_matched %>% filter(cov_grp==1)

covs <- post_omicron  %>% 
  select(encAge,gender,raceEthnicity,dischargeLocation2,encDeathDerived,
         dischargeDispositionGroup2,prevDischarge90Days,LOS,facility_admission,
         starts_with("elix_"),
         maxTemp,medRR,medSBP,medDBP,maxALT,maxTBILI,minALB,minSODIUM,maxCREAT,
         minPLT,maxWBC,minHCT,maxGLU,ICUalgo,serviceGroup2,ttmatch_days,matchtodischarge_days,
         covVaxEver,covVaxLast4months,covVaxCumSum)

bal.tab(case ~ covs, data = post_omicron, binary = "std", continuous = "std")
```


## Outcomes
```{r,include=FALSE}
# make a copy of matched data 
covid_data_simulation_matched2 <- covid_data_simulation_matched %>% 
  group_by(matches) %>% 
  mutate(hospitalDay_normalized = hospitalDay-min(hospitalDay), 
         hospitalDay0_normalized = hospitalDay0-min(hospitalDay))

nrow(distinct(covid_data_simulation_matched2,matchid))
nrow(distinct(covid_data_simulation_matched2,matches))
```


```{r}
new_event_after_match_HR <- function(indata,eventLBL,tp) {
  
  if (tp=="pre-omicron"){
    neweventdat <- indata %>% filter(cov_grp==0)
  } else {
    neweventdat <- indata %>% filter(cov_grp==1)
  }
  
  # Cox proportional hazards regression
  fit <- coxph(Surv(event_T, event_flg) ~ case, data = neweventdat, cluster = matchid)
  
  print(summary(fit))
  
  out <- fit %>%  
  tidy(conf.int = TRUE, exponentiate = TRUE) %>% 
  select(estimate, starts_with("conf"),p.value)
  
  ##############
  #UPDATED: Tom#
  out <- out %>% mutate(event=eventLBL, metric = "Hazard ratio")
  ##############
  
  if (tp=="pre-omicron"){
    out <- out %>% 
      rename(po_estimate=estimate,po_conf_low=conf.low,po_conf_high=conf.high,po_pvalue=p.value)
} else {
    out <- out %>% 
      rename(o_estimate=estimate,o_conf_low=conf.low,o_conf_high=conf.high,o_pvalue=p.value)
}
  
  return(out)
}

##############
#UPDATED: Tom#
coefSmry.lm <- function(in_testcoef,tp,eventLBL){
  
  if (tp=="pre-omicron"){
    out <- data.frame(event=eventLBL,
                      po_estimate=in_testcoef[2], 
                      po_conf_low=in_testcoef[10],
                      po_conf_high=in_testcoef[12],
                      po_pvalue= in_testcoef[8],
                      metric = "Difference")
} else {
    out <- data.frame(event=eventLBL,
                      o_estimate=in_testcoef[2], 
                      o_conf_low=in_testcoef[10],
                      o_conf_high=in_testcoef[12],
                      o_pvalue= in_testcoef[8],
                      metric = "Difference")
}
  return(out)
}
##############

##############
#UPDATED: Tom#
coefSmry.glmbinomial <- function(in_testcoef,tp,eventLBL){
  
  if (tp=="pre-omicron"){
    out <- data.frame(event=eventLBL,
                      po_estimate=exp(in_testcoef[2]), 
                      po_conf_low=exp(in_testcoef[10]),
                      po_conf_high=exp(in_testcoef[12]),
                      po_pvalue= in_testcoef[8],
                      metric = "Relative Risk")
} else {
    out <- data.frame(event=eventLBL,
                      o_estimate=exp(in_testcoef[2]), 
                      o_conf_low=exp(in_testcoef[10]),
                      o_conf_high=exp(in_testcoef[12]),
                      o_pvalue= in_testcoef[8],
                      metric = "Relative Risk")
}
  return(out)
}

##############

##############
#UPDATED: Tom#
coefSmry_cox <- function(fit,tp,eventLBL){
  
  out <- fit %>%  
  tidy(conf.int = TRUE, exponentiate = TRUE) %>% 
  select(estimate, starts_with("conf"),p.value)
  
  out <- out %>% mutate(event=eventLBL, metric = "Hazard ratio")
  
  if (tp=="pre-omicron"){
    out <- out %>% 
      rename(po_estimate=estimate,po_conf_low=conf.low,po_conf_high=conf.high,po_pvalue=p.value)
} else {
    out <- out %>% 
      rename(o_estimate=estimate,o_conf_low=conf.low,o_conf_high=conf.high,o_pvalue=p.value)
}
  
  return(out)
}
##############

pre_omicron <- covid_data_simulation_matched2 %>% filter(cov_grp==0)
post_omicron <- covid_data_simulation_matched2 %>% filter(cov_grp==1)

```

### RR Function ###
```{r}
new_outcome_RR <- function(indata,eventLBL,tp) {
  
   if (tp=="pre-omicron"){
    neweventdat <- indata %>% filter(cov_grp==0)
  } else {
    neweventdat <- indata %>% filter(cov_grp==1)
  }
  
  mod = glm(event_flg ~ case,data =neweventdat, family = binomial(link = "log"))
  
  fit <- cbind(coeftest(mod, vcov = vcovCL, cluster = ~matchid), coefci(mod, vcov = vcovCL, cluster = ~matchid))
  
  out <- coefSmry.glmbinomial(fit,tp,eventLBL)
  
}
```


### New admission to ICU After Match Day (HR) ###
```{r}
new_events_icu <- new_events %>% 
  select(hospID,matchid,case,cov_grp,event_T=after_match_new_icu_T,event_flg=after_match_new_icu)
  
newICU_po <- new_event_after_match_HR(new_events_icu,"New admission to ICU After Match Day","pre-omicron")

# Post-Omicron
newICU_o <- new_event_after_match_HR(new_events_icu,"New admission to ICU After Match Day","omicron")

newICU <- full_join(newICU_po,newICU_o, by = "event")
```

### New admission to ICU After Match Day (RR) ###
```{r}
new_icu_po = new_outcome_RR(new_events_icu,"New admission to ICU After Match Day (Relative Risk)","pre-omicron")

new_icu_o = new_outcome_RR(new_events_icu,"New admission to ICU After Match Day (Relative Risk)","omicron")


new_icu_RR <- full_join(new_icu_po,new_icu_o,by="event")

```

### New Need for High Flow O2 After Match Day (HR) ###
```{r}
new_events_HF <- new_events %>% 
  select(hospID,matchid,case,cov_grp,event_T=after_match_new_hf_T,event_flg=after_match_new_hf)
  
# Pre-Omicron
newHF_po <- new_event_after_match_HR(new_events_HF,"New Need for High Flow O2 After Match Day","pre-omicron")

# Post-Omicron
newHF_o <- new_event_after_match_HR(new_events_HF,"New Need for High Flow O2 After Match Day","omicron")

newHF <- full_join(newHF_po,newHF_o, by = "event")
```

### New Need for High Flow O2 After Match Day (RR) ###
```{r}

new_hf_po = new_outcome_RR(new_events_HF,"New Need for High Flow O2 After Match Day (Relative Risk)","pre-omicron")

new_hf_o = new_outcome_RR(new_events_HF,"New Need for High Flow O2 After Match Day (Relative Risk)","omicron")


new_hf_RR <- full_join(new_hf_po,new_hf_o,by="event")
```

### New Need for BIPAP After Match Day (HR) ###
```{r}
new_events_BIPAP <- new_events %>% 
  select(hospID,matchid,case,cov_grp,event_T=after_match_new_bipap_T,event_flg=after_match_new_bipap)

# Pre-Omicron
newBIPAP_po <- new_event_after_match_HR(new_events_BIPAP,"New Need for BIPAP After Match Day","pre-omicron")

# Post-Omicron
newBIPAP_o <- new_event_after_match_HR(new_events_BIPAP,"New Need for BIPAP After Match Day","omicron")

newBIPAP <- full_join(newBIPAP_po,newBIPAP_o, by = "event")
```

### New Need for BIPAP After Match Day (RR) ###
```{r}
new_bipap_po = new_outcome_RR(new_events_BIPAP,"New Need for BIPAP After Match Day (Relative Risk)","pre-omicron")

new_bipap_o = new_outcome_RR(new_events_BIPAP,"New Need for BIPAP After Match Day (Relative Risk)","omicron")

new_bipap_RR <- full_join(new_bipap_po,new_bipap_o,by="event")
```

### New Need for Mechanical Ventilation After Match Day (HR) ###
```{r}
new_events_VENT <- new_events %>% 
  select(hospID,matchid,case,cov_grp,event_T=after_match_new_vent_T,event_flg=after_match_new_vent)


newVent_po  <- new_event_after_match_HR(new_events_VENT,"New Need for Mechanical Ventilation After Match Day","pre-omicron")


newVent_o <-  new_event_after_match_HR(new_events_VENT,"New Need for Mechanical Ventilation After Match Day","omicron")

newVent <- full_join(newVent_po,newVent_o, by = "event")
```

### New Need for Mechanical Ventilation After Match Day (RR) ###
```{r}
new_vent_po = new_outcome_RR(new_events_VENT,"New Need for Mechanical Ventilation After Match Day (Relative Risk)","pre-omicron")

new_vent_o = new_outcome_RR(new_events_VENT,"New Need for Mechanical Ventilation After Match Day (Relative Risk)","omicron")
##############

new_vent_RR <- full_join(new_vent_po,new_vent_o,by="event")
```

### New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day (HR) ###
```{r}
new_events_O2 <- new_events %>% 
  select(hospID,matchid,case,cov_grp,event_T=after_match_new_hfbipapvent_T,event_flg=after_match_new_hfbipapvent)

newO2_po  <-   new_event_after_match_HR(new_events_O2, "New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day","pre-omicron")


newO2_o <-  new_event_after_match_HR(new_events_O2, "New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day","omicron")

newO2 <- full_join(newO2_po,newO2_o, by = "event")
```

### New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day (RR) ###
```{r}
new_o2_po = new_outcome_RR(new_events_O2,"New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day (Relative Risk)","pre-omicron")

new_o2_o = new_outcome_RR(new_events_O2,"New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day (Relative Risk)","omicron")

new_o2_RR <- full_join(new_o2_po,new_o2_o,by="event")
```

### Days from Match Day to Discharge ###
```{r}
covid_data_simulation_matched3 <- pre_omicron %>% 
  mutate(match_to_discharge_days= as.numeric(dischargeDT-date)+1)

# Pre-Omicron
mtdM <- lm(match_to_discharge_days ~ case, data = covid_data_simulation_matched3)
testcoef = cbind(coeftest(mtdM, vcov = vcovCL, cluster = ~matchid),coefci(mtdM, vcov = vcovCL, cluster = ~matchid))
testcoef

##############
#UPDATED: Tom#
mtd_po <-coefSmry.lm(testcoef,"pre-omicron","Days from Match Day to Discharge")
##############

covid_data_simulation_matched3 <- post_omicron %>% 
  mutate(match_to_discharge_days= as.numeric(dischargeDT-date)+1)

# Post-Omicron
mtdM <- lm(match_to_discharge_days ~ case, data = covid_data_simulation_matched3)
testcoef = cbind(coeftest(mtdM, vcov = vcovCL, cluster = ~matchid),coefci(mtdM, vcov = vcovCL, cluster = ~matchid))
testcoef

##############
#UPDATED: Tom#
mtd_o <-coefSmry.lm(testcoef,"omicron","Days from Match Day to Discharge")
##############

mtd = full_join(mtd_po,mtd_o, by = "event")
```

### Hospital Length of Stay ###
```{r}
# Pre-Omicron
losM <- lm(LOS ~ case, data = pre_omicron)
testcoef = cbind(coeftest(losM, vcov = vcovCL, cluster = ~matchid),coefci(losM, vcov = vcovCL, cluster = ~matchid))
testcoef

##############
#UPDATED: Tom#
los_po <-coefSmry.lm(testcoef,"pre-omicron","Hospital Length of Stay")
##############

# Post-Omicron
losM <- lm(LOS ~ case, data = post_omicron)
testcoef = cbind(coeftest(losM, vcov = vcovCL, cluster = ~matchid),coefci(losM, vcov = vcovCL, cluster = ~matchid))
testcoef

##############
#UPDATED: Tom#
los_o <-coefSmry.lm(testcoef,"omicron","Hospital Length of Stay")
##############

los = full_join(los_po,los_o, by = "event")
```


### Hospital Length of Stay (Survivors Only) ###
```{r}
# Pre-Omicron
pre_omicron_surv <- pre_omicron %>% filter(encDeathDerived==0)
losM <- lm(LOS ~ case, data = pre_omicron_surv)
testcoef = cbind(coeftest(losM, vcov = vcovCL, cluster = ~matchid),coefci(losM, vcov = vcovCL, cluster = ~matchid))
testcoef

##############
#UPDATED: Tom#
los_po <-coefSmry.lm(testcoef,"pre-omicron","Hospital Length of Stay (Survivors Only)")
##############

# Post-Omicron
post_omicron_surv <- post_omicron %>% filter(encDeathDerived==0)
losM <- lm(LOS ~ case, data = post_omicron_surv)
testcoef = cbind(coeftest(losM, vcov = vcovCL, cluster = ~matchid),coefci(losM, vcov = vcovCL, cluster = ~matchid))
testcoef

##############
#UPDATED: Tom#
los_o <-coefSmry.lm(testcoef,"omicron","Hospital Length of Stay (Survivors Only)")
##############

los_survivors = full_join(los_po,los_o, by = "event")
```

### Discharge to Home ### 
```{r}
dcHomedsn <- covid_data_simulation %>% 
  mutate(dc_T = LOS,
         dc_Flg = ifelse(discharge_home==1, 1, 0)) %>% 
  distinct(hospID,dc_T,dc_Flg)

# Pre-Omicron
covid_data_simulation_matched3 <- left_join(pre_omicron ,dcHomedsn, by="hospID")

# Cox proportional hazards regression
fit = coxph(Surv(dc_T, dc_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

dth_po = coefSmry_cox(fit,"pre-omicron","Discharge to Home")

# Post-Omicron
covid_data_simulation_matched3 <- left_join(post_omicron,dcHomedsn,by="hospID")

# Cox proportional hazards regression
fit = coxph(Surv(dc_T, dc_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

dth_o = coefSmry_cox(fit,"omicron","Discharge to Home")

dth <- full_join(dth_po,dth_o, by = "event")
```

### Discharge to Home (RR) ###
```{r}
outcome <- function(indata) { 
covid_data_simulation_matched3 <- indata 

mod = glm(discharge_home ~ case,data =covid_data_simulation_matched3, family = binomial(link = "log"))
cbind(coeftest(mod, vcov = vcovCL, cluster = ~matchid), coefci(mod, vcov = vcovCL, cluster = ~matchid))
}

# Pre-Omicron
fit <- outcome(covid_data_simulation_matched2 %>% filter(cov_grp==0))
fit

##############
#UPDATED: Tom#
dc_home_po = coefSmry.glmbinomial(fit,"pre-omicron","Discharge to Home (Relative Risk)")
##############

# post-Omicron
fit <- outcome(covid_data_simulation_matched2 %>% filter(cov_grp==1))
fit

##############
#UPDATED: Tom#
dc_home_o = coefSmry.glmbinomial(fit,"omicron","Discharge to Home (Relative Risk)")
##############

dc_home_RR <- full_join(dc_home_po,dc_home_o,by="event")
```

### Discharge to Rehab ###
```{r}
dcRehabdsn <- covid_data_simulation %>% 
  mutate(dc_T = LOS,
         dc_Flg = ifelse(discharge_rehab==1, 1, 0)) %>% 
  distinct(hospID,dc_T,dc_Flg)

# Pre-Omicron
covid_data_simulation_matched3 <- left_join(pre_omicron ,dcRehabdsn, by="hospID")
# Cox proportional hazards regression
fit = coxph(Surv(dc_T, dc_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

dtr_po = coefSmry_cox(fit,"pre-omicron","Discharge to Rehab")

# Post-Omicron
covid_data_simulation_matched3 <- left_join(post_omicron ,dcRehabdsn, by="hospID")
# Cox proportional hazards regression
fit = coxph(Surv(dc_T, dc_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

dtr_o = coefSmry_cox(fit,"omicron","Discharge to Rehab")

dtr <- full_join(dtr_po,dtr_o, by = "event")
```

### Discharge to Rehab (RR) ###
```{r}
outcome <- function(indata) { 
covid_data_simulation_matched3 <- indata 

mod = glm(discharge_rehab ~ case,data =covid_data_simulation_matched3, family = binomial(link = "log"))
cbind(coeftest(mod, vcov = vcovCL, cluster = ~matchid), coefci(mod, vcov = vcovCL, cluster = ~matchid))
}

# Pre-Omicron
fit <- outcome(covid_data_simulation_matched2 %>% filter(cov_grp==0))
fit

##############
#UPDATED: Tom#
dc_rehab_po = coefSmry.glmbinomial(fit,"pre-omicron","Discharge to Rehab (Relative Risk)")
##############

# post-Omicron
fit <- outcome(covid_data_simulation_matched2 %>% filter(cov_grp==1))
fit

##############
#UPDATED: Tom#
dc_rehab_o = coefSmry.glmbinomial(fit,"omicron","Discharge to Rehab (Relative Risk)")
##############

dc_rehab_RR <- full_join(dc_rehab_po,dc_rehab_o,by="event")
```

### Discharge to SNF ###
```{r}
dcSNFdsn <- covid_data_simulation %>% 
  mutate(dc_T = LOS,
         dc_Flg = ifelse(discharge_snf==1, 1, 0)) %>% 
  distinct(hospID,dc_T,dc_Flg)

# Pre-Omicron
covid_data_simulation_matched3 <- left_join(pre_omicron ,dcSNFdsn, by="hospID")

# Cox proportional hazards regression
fit <- coxph(Surv(dc_T, dc_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

dtsnf_po = coefSmry_cox(fit,"pre-omicron","Discharge to SNF")

# Post-Omicron
covid_data_simulation_matched3 <- left_join(post_omicron ,dcSNFdsn, by="hospID")

# Cox proportional hazards regression
fit <- coxph(Surv(dc_T, dc_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

dtsnf_o = coefSmry_cox(fit,"omicron","Discharge to SNF")

dtsnf <- full_join(dtsnf_po,dtsnf_o, by = "event")
```

### Discharge to SNF (RR) ###
```{r}
outcome <- function(indata) { 
covid_data_simulation_matched3 <- indata 

mod = glm(discharge_snf ~ case,data =covid_data_simulation_matched3, family = binomial(link = "log"))
cbind(coeftest(mod, vcov = vcovCL, cluster = ~matchid), coefci(mod, vcov = vcovCL, cluster = ~matchid))
}

# Pre-Omicron
fit <- outcome(covid_data_simulation_matched2 %>% filter(cov_grp==0))
fit

##############
#UPDATED: Tom#
dc_snf_po = coefSmry.glmbinomial(fit,"pre-omicron","Discharge to SNF (Relative Risk)")
##############

# post-Omicron
fit <- outcome(covid_data_simulation_matched2 %>% filter(cov_grp==1))
fit

##############
#UPDATED: Tom#
dc_snf_o = coefSmry.glmbinomial(fit,"omicron","Discharge to SNF (Relative Risk)")
##############

dc_snf_RR <- full_join(dc_snf_po,dc_snf_o,by="event")
```

### Discharge to Hospice ###
```{r}
dcHospicedsn <- covid_data_simulation %>% 
  mutate(dc_T = LOS,
         dc_Flg = ifelse(discharge_hospice==1, 1, 0)) %>% 
  distinct(hospID,dc_T,dc_Flg)

# Pre-Omicron
covid_data_simulation_matched3 <- left_join(pre_omicron ,dcHospicedsn, by="hospID")

# Cox proportional hazards regression
fit <- coxph(Surv(dc_T, dc_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

dthospice_po = coefSmry_cox(fit,"pre-omicron","Discharge to Hospice")

# Post-Omicron
covid_data_simulation_matched3 <- left_join(post_omicron ,dcHospicedsn, by="hospID")

# Cox proportional hazards regression
fit <- coxph(Surv(dc_T, dc_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

dthospice_o = coefSmry_cox(fit,"omicron","Discharge to Hospice")

dthospice <- full_join(dthospice_po,dthospice_o, by = "event")
```

### Discharge to Hospice (RR) ###
```{r}
outcome <- function(indata) { 
covid_data_simulation_matched3 <- indata 

mod = glm(discharge_hospice ~ case,data =covid_data_simulation_matched3, family = binomial(link = "log"))
cbind(coeftest(mod, vcov = vcovCL, cluster = ~matchid), coefci(mod, vcov = vcovCL, cluster = ~matchid))
}

# Pre-Omicron
fit <- outcome(covid_data_simulation_matched2 %>% filter(cov_grp==0))
fit

##############
#UPDATED: Tom#
dc_hospice_po = coefSmry.glmbinomial(fit,"pre-omicron","Discharge to Hospice (Relative Risk)")
##############

# post-Omicron
fit <- outcome(covid_data_simulation_matched2 %>% filter(cov_grp==1))
fit

##############
#UPDATED: Tom#
dc_hospice_o = coefSmry.glmbinomial(fit,"omicron","Discharge to Hospice (Relative Risk)")
##############

dc_hospice_RR <- full_join(dc_hospice_po,dc_hospice_o,by="event")
```

### Discharge to Hospice - Subdistributional Hazard ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
   mutate(
         dd2 = case_when(
           dischargeDispositionGroup2=="Hospice" ~ 1,
           dischargeDispositionGroup2=="Rehabilitation facility" ~ 2,
           dischargeDispositionGroup2=="Skilled nursing facility" ~ 3,
           dischargeDispositionGroup2=="Other" ~ 4,
           dischargeDispositionGroup2=="Death" ~ 5,
           dischargeDispositionGroup2=="Home" ~ 6,
         ),
         
         dd2 = factor(dd2, levels = c(0,1,2,3,4,5,6),
                            labels = c("Nothing","Hospice","Rehabilitation facility","Skilled nursing facility","Other","Death","Home")))

str(covid_data_simulation_matched3$dd2)

covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)


# Pre-Omicron
po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)

# Code does not work when using etype
# It looks like the default for finegray is to use the first value
subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=po)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

hospice_sh_po <- coefSmry_cox(fgfit,"pre-omicron","Discharge to Hospice - Subdistributional Hazard")

# post-Omicron
o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=o)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

hospice_sh_o <- coefSmry_cox(fgfit,"omicron","Discharge to Hospice - Subdistributional Hazard")

hospice_sh <- full_join(hospice_sh_po,hospice_sh_o,by="event")
```

### Discharge to Hospice or Death ###
```{r}
encdeathdsn <- covid_data_simulation %>% 
  mutate(death_T = LOS,
         death_Flg = ifelse(encDeathDerived==1 | dischargeDispositionGroup2=="Hospice", 1, 0)) %>% 
  distinct(hospID,death_T,death_Flg)

# Pre-Omicron
covid_data_simulation_matched3 <- left_join(pre_omicron ,encdeathdsn, by="hospID")

# Cox proportional hazards regression
fit <- coxph(Surv(death_T, death_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

deathospice_po = coefSmry_cox(fit,"pre-omicron","Discharge to Hospice or Death")


# Post-Omicron
covid_data_simulation_matched3 <- left_join(post_omicron ,encdeathdsn, by="hospID")

# Cox proportional hazards regression
fit <- coxph(Surv(death_T, death_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

deathospice_o = coefSmry_cox(fit,"omicron","Discharge to Hospice or Death")

deathospice <- full_join(deathospice_po,deathospice_o, by = "event")
```


### Discharge to Hospice or Death - Subdistributional Hazard ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
  mutate(
         dd2 = case_when(
           encDeathDerived==1 | dischargeDispositionGroup2=="Death" | dischargeDispositionGroup2=="Hospice" ~ 1,
           dischargeDispositionGroup2=="Rehabilitation facility" ~ 2,
           dischargeDispositionGroup2=="Skilled nursing facility" ~ 3,
           dischargeDispositionGroup2=="Other" ~ 4,
           dischargeDispositionGroup2== "Home" ~ 5,
         ),
         
         dd2 = factor(dd2, levels = c(0,1,2,3,4,5),
                            labels = c("Nothing","Death/Hospice","Rehabilitation facility","Skilled nursing facility","Other","Home")))

str(covid_data_simulation_matched3$dd2)

covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)

# Pre-Omicron
po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)

# Code does not work when using etype
# It looks like the default for finegray is to use the first value
subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=po)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

deathhospice_sh_po <- coefSmry_cox(fgfit,"pre-omicron","Discharge to Hospice or Death - Subdistributional Hazard")

# post-Omicron
o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=o)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

deathhospice_sh_o <- coefSmry_cox(fgfit,"omicron","Discharge to Hospice or Death - Subdistributional Hazard")

deathhospice_sh <- full_join(deathhospice_sh_po,deathhospice_sh_o,by="event")
```


### Discharged Alive (Home, SNF, Rehab, Hospice, Other) - Subdistributional Hazard ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
  mutate(
         dd2 = case_when(
           dischargeDispositionGroup2=="Home" | dischargeDispositionGroup2=="Hospice" | dischargeDispositionGroup2=="Rehabilitation facility" | dischargeDispositionGroup2=="Skilled nursing facility" | dischargeDispositionGroup2=="Other" ~ 1,
           dischargeDispositionGroup2=="Death" ~ 2
         ),
         
         dd2 = factor(dd2, levels = c(0,1,2),
                            labels = c("Nothing","Discharged Alive","Death")))

str(covid_data_simulation_matched3$dd2)

covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)

# Pre-Omicron
po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)

# Code does not work when using etype
# It looks like the default for finegray is to use the first value
subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=po)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

dcalive_sh_po <- coefSmry_cox(fgfit,"pre-omicron","Discharged Alive (Home, SNF, Rehab, Hospice, Other) - Subdistributional Hazard")

# post-Omicron
o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=o)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

dcalive_sh_o <- coefSmry_cox(fgfit,"omicron","Discharged Alive (Home, SNF, Rehab, Hospice, Other) - Subdistributional Hazard")

dcalive_sh <- full_join(dcalive_sh_po,dcalive_sh_o,by="event")
```

### Discharged Alive (Home, SNF, Rehab, Other) - Subdistributional Hazard ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
  mutate(
         dd2 = case_when(
           dischargeDispositionGroup2=="Home" | dischargeDispositionGroup2=="Rehabilitation facility" | dischargeDispositionGroup2=="Skilled nursing facility" | dischargeDispositionGroup2=="Other" ~ 1,
           dischargeDispositionGroup2=="Death" ~ 2,
           dischargeDispositionGroup2=="Hospice" ~ 3
         ),
         
         dd2 = factor(dd2, levels = c(0,1,2,3),
                            labels = c("Nothing","Discharged Alive","Death","Hospice")))

str(covid_data_simulation_matched3$dd2)

covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)

# Pre-Omicron
po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)

# Code does not work when using etype
# It looks like the default for finegray is to use the first value
subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=po)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

dcalive2_sh_po <- coefSmry_cox(fgfit,"pre-omicron","Discharged Alive (Home, SNF, Rehab, Other) - Subdistributional Hazard")

# post-Omicron
o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=o)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

dcalive2_sh_o <- coefSmry_cox(fgfit,"omicron","Discharged Alive (Home, SNF, Rehab, Other) - Subdistributional Hazard")

dcalive2_sh <- full_join(dcalive2_sh_po,dcalive2_sh_o,by="event")
```

### Discharged To Facility (SNF, Rehab, Hospice) - Subdistributional Hazard ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
  mutate(
         dd2 = case_when(
            dischargeDispositionGroup2=="Rehabilitation facility" | dischargeDispositionGroup2=="Skilled nursing facility" | dischargeDispositionGroup2=="Hospice" ~ 1,
           dischargeDispositionGroup2=="Death" ~ 2,
           dischargeDispositionGroup2=="Home"  ~ 3,
           dischargeDispositionGroup2=="Other" ~ 4
         ),
         
         dd2 = factor(dd2, levels = c(0,1,2,3,4),
                            labels = c("Nothing","Facility","Death","Home","Other")))

str(covid_data_simulation_matched3$dd2)

covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)

# Pre-Omicron
po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)

# Code does not work when using etype
# It looks like the default for finegray is to use the first value
subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=po)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

dcfacility_sh_po <- coefSmry_cox(fgfit,"pre-omicron","Discharged To Facility (SNF, Rehab, Hospice) - Subdistributional Hazard")

# post-Omicron
o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=o)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

dcfacility_sh_o <- coefSmry_cox(fgfit,"omicron","Discharged To Facility (SNF, Rehab, Hospice) - Subdistributional Hazard")

dcfacility_sh <- full_join(dcfacility_sh_po,dcfacility_sh_o,by="event")
```

### Hospital Death ###
```{r}
encdeathdsn <- covid_data_simulation %>% 
  mutate(death_T = LOS,
         death_Flg = ifelse(encDeathDerived==1, 1, 0)) %>% 
  distinct(hospID,death_T,death_Flg)

# Pre-Omicron
covid_data_simulation_matched3 <- left_join(pre_omicron ,encdeathdsn, by="hospID")

# Cox proportional hazards regression
fit <- coxph(Surv(death_T, death_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

hospdeath_po = coefSmry_cox(fit,"pre-omicron","Hospital Death")


# Post-Omicron
covid_data_simulation_matched3 <- left_join(post_omicron ,encdeathdsn, by="hospID")

# Cox proportional hazards regression
fit <- coxph(Surv(death_T, death_Flg) ~ case, data = covid_data_simulation_matched3, cluster = matchid)
summary(fit)

hospdeath_o = coefSmry_cox(fit,"omicron","Hospital Death")

hospdeath <- full_join(hospdeath_po,hospdeath_o, by = "event")
```

### Hospital Death - Subdistributional Hazard ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
  mutate(dd2 = case_when(
           encDeathDerived==1 | dischargeDispositionGroup2=="Death" ~ 1,
           dischargeDispositionGroup2== "Home" ~ 2,
           dischargeDispositionGroup2=="Rehabilitation facility" ~ 3,
           dischargeDispositionGroup2=="Skilled nursing facility" ~ 4,
           dischargeDispositionGroup2=="Other" ~ 5,
           dischargeDispositionGroup2=="Hospice" ~ 6
         ),
         
         dd2 = factor(dd2, levels = c(0,1,2,3,4,5,6),
                            labels = c("Nothing","Death","Home","Rehabilitation facility","Skilled nursing facility","Other","Hospice")))

str(covid_data_simulation_matched3$dd2)

covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)


# Pre-Omicron
po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)

# Code does not work when using etype
# It looks like the default for finegray is to use the first value
subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=po)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

hospdeath_sh_po <- coefSmry_cox(fgfit,"pre-omicron","Hospital Death - Subdistributional Hazard")

# post-Omicron
o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

subdistdat = finegray(Surv(LOS, dd2) ~ case, 
                      data=o)

fgfit <- coxph(Surv(fgstart, fgstop, fgstatus) ~ case,
               weight=fgwt, data=subdistdat)

summary(fgfit)

hospdeath_sh_o <- coefSmry_cox(fgfit,"omicron","Hospital Death - Subdistributional Hazard")

hospdeath_sh <- full_join(hospdeath_sh_po,hospdeath_sh_o,by="event")
```



### 30-day Mortality (counting from match day) ###
```{r}
max_admitDT <- max(covid_data_simulation$admitDT)

outcome_death30day <- function(indata) { 
covid_data_simulation_matched3 <- indata %>% 
  # only look at hospitalization that could have data 30 days post discharge
  filter(dischargeDT<=max_admitDT-30) %>% 
  mutate(deathDT_derived = date(deathDTS_derived),
         match_to_death_days = as.numeric((deathDT_derived - date) +1),
         death30day = if_else(!is.na(match_to_death_days) & match_to_death_days <= 30, 1, 0))

# N cases after filtering
nrow(covid_data_simulation_matched3 %>% filter(case==1))

mod = glm(death30day ~ case,data =covid_data_simulation_matched3, family = binomial(link = "log"))
cbind(coeftest(mod, vcov = vcovCL, cluster = ~matchid), coefci(mod, vcov = vcovCL, cluster = ~matchid))
}

# Pre-Omicron
fit <- outcome_death30day(covid_data_simulation_matched2 %>% filter(cov_grp==0))
fit

##############
#UPDATED: Tom#
death30day_po = coefSmry.glmbinomial(fit,"pre-omicron","30-day Mortality (counting from match day)")
##############

# post-Omicron
fit <- outcome_death30day(covid_data_simulation_matched2 %>% filter(cov_grp==1))
fit

##############
#UPDATED: Tom#
death30day_o = coefSmry.glmbinomial(fit,"omicron","30-day Mortality (counting from match day)")
##############

death30day <- full_join(death30day_po,death30day_o,by="event")
```

### Hospital Death (RR) ###
```{r}

outcome_hospital_death <- function(indata) { 
covid_data_simulation_matched3 <- indata %>% 
  mutate(dd2 = if_else(encDeathDerived==1 | dischargeDispositionGroup2=="Death", "Death",dischargeDispositionGroup2),
         hospital_death= if_else(dd2=="Death",1,0))


mod = glm(hospital_death ~ case,data =covid_data_simulation_matched3, family = binomial(link = "log"))
cbind(coeftest(mod, vcov = vcovCL, cluster = ~matchid), coefci(mod, vcov = vcovCL, cluster = ~matchid))
}

# Pre-Omicron
fit <- outcome_hospital_death(covid_data_simulation_matched2 %>% filter(cov_grp==0))
fit

##############
#UPDATED: Tom#
hospital_death_po = coefSmry.glmbinomial(fit,"pre-omicron","Hospital Death (Relative Risk)")
##############

# post-Omicron
fit <- outcome_hospital_death(covid_data_simulation_matched2 %>% filter(cov_grp==1))
fit

##############
#UPDATED: Tom#
hospital_death_o = coefSmry.glmbinomial(fit,"omicron","Hospital Death (Relative Risk)")
##############

hospital_death_RR <- full_join(hospital_death_po,hospital_death_o,by="event")
```

### 30-day Readmission (counting from match day) ###
```{r}
outcome_readmit30day <- function(indata) { 
  covid_data_simulation_matched3 <- indata %>% 
  # only look at hospitalization that could have data 30 days post discharge
  filter(dischargeDT<=max_admitDT-30) %>% 
  mutate(nextAdmitDT = date(nextAdmitDTS),
         match_to_next_admit_days = as.numeric((nextAdmitDT - date)+1),
         readmit30day = if_else(!is.na(match_to_next_admit_days) & match_to_next_admit_days <= 30, 1, 0))

# N cases after filtering
print(nrow(covid_data_simulation_matched3 %>% filter(case==1)))


mod = glm(readmit30day ~ case,data =covid_data_simulation_matched3, family = binomial(link = "log"))
cbind(coeftest(mod, vcov = vcovCL, cluster = ~matchid),coefci(mod, vcov = vcovCL, cluster = ~matchid))

}

# Pre-Omicron
fit <- outcome_readmit30day(covid_data_simulation_matched2 %>% filter(cov_grp==0))
fit

##############
#UPDATED: Tom#
readmit30day_po = coefSmry.glmbinomial(fit,"pre-omicron","30-day Readmission (counting from match day)")
##############

# post-Omicron
fit <- outcome_readmit30day(covid_data_simulation_matched2 %>% filter(cov_grp==1))
fit

##############
#UPDATED: Tom#
readmit30day_o = coefSmry.glmbinomial(fit,"omicron","30-day Readmission (counting from match day)")
##############

readmit30day <- full_join(readmit30day_po,readmit30day_o,by="event")
```

### Outcome Summary ###
```{r}
os  <-   bind_rows(newICU,new_icu_RR,newHF,new_hf_RR,newBIPAP,new_bipap_RR,newVent,new_vent_RR,
                   newO2,new_o2_RR,mtd,los,los_survivors,dth,dc_home_RR,dtr,dc_rehab_RR,
                   dtsnf,dc_snf_RR,dthospice,dc_hospice_RR,hospice_sh,deathospice,deathhospice_sh,
                   dcalive_sh,dcalive2_sh,dcfacility_sh,hospdeath,hospdeath_sh,hospital_death_RR,
                   death30day,readmit30day) %>% select(event,everything())

write.csv(os,file = file.path(outLoc,paste0("outcomes_",outfilesfx,".csv")))


kable(os,
      digits = c(2,2, 2, 2,3,2, 2, 2,3),
      format.args = list(scientific = FALSE))

```

