---
title: Hospital-Acquired SARS-CoV-2
subtitle: Exact Match, Followed by Propensity Score Matching Analysis, Adjusted Relative Risk Outcomes
author: 
date: 
output:
  word_document:
    reference_docx: word_styles.docx
    df_print: kable
  html_document: default
  pdf_document: default
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_file = 'ho_COVID_vax_status_RR_adjust_2024-05-22.docx',
      envir = globalenv()
    )
  })
---

```{r,include=FALSE}
library(tidyverse)
library(survival)
library(ipw)
library(optmatch)
library(lubridate)
library(MatchIt)
library(naniar)
library(lmtest)
library(RItools)
library(sandwich)
library(broom)
library(knitr)
library(cobalt)
library(quantreg)

filesfx <- "vax_status_2024-05-08"
outfilesfx <- "vax_status_RR_adjust_2024-05-22"

loc <- "/data/tide/projects/ho-covid/annals_resubmission/add_addtl_vars_dr5_sdm/sensitivity_analyses/vax_status"

dataLoc <- paste0(loc,"/data")
outLoc <- paste0(loc,"/output")


# setwd("/external/BWH-ICRESEARCH/Projects/Hospital Onset COVID")
covid_data_simulation <- readRDS(file.path(dataLoc,paste0("covid_data_simulation_",filesfx,".Rds")))
matchedF <- paste0("covid_data_simulation_matched_",filesfx,".Rds")

new_events <- readRDS(file.path(dataLoc,"ho_covid_after_match_new_events_vax_status_2024-05-22.Rds")) %>% select(-case,-cov_grp)

# after_match_new_events <- new_events %>% 
#   select(hospID,matchid,hospitalfree30day)
```
  
## Inclusion Criteria
Patients were included in analysis if they met **all** of the following criteria:
  
- Admission to BWH, MGH, BWF, NSMC, NWH on or after December 1, 2020 through April 30, 2023
- Age >= 18
- Hospital length of stay >= 5 days

## Exclusions
Patients were excluded from analysis if they met **any** of the following criteria:
  
- COVID flag active on hospital day 1 - 4


## Case Definition
Cases were defined as:
  
- Activation of COVID-19 flag on hospital day 5 or greater
- COVID-19 flag remains active for >= 4 days (including post-discharge)


## Study Population
```{r}
# N Hospitalizations
nrow(distinct(covid_data_simulation,hospID))

# Min Admit Date
min(covid_data_simulation$admitDT)

# Max Admit Date
max(covid_data_simulation$admitDT)

# N Hospital Days
nrow(covid_data_simulation)

# N Cases
nrow(covid_data_simulation %>% filter(case==1))
```


## Matching
Cases are matched to controls in three steps.

1. Exact match on:

- Hospital
- Service group on match day minus 2
- ICU status on match day minus 2

2. Caliper match on:
- LOS for controls greater than or equal to match day for case
- Admit date within 90 days
- Propensity score standardized difference  < 0.2


```{r}
covid_data_simulation_matched <- readRDS(file.path(dataLoc,matchedF)) %>%
  left_join(.,new_events,by=c("hospID","matchid")) %>% 
   mutate(ttmatch_days= as.numeric((date-admitDT)+1),
         matchtodischarge_days= as.numeric(dischargeDT-date))

# N matches
nrow(distinct(covid_data_simulation_matched,matchid))
```

## Balance Results Using Cobalt 
### Pre-Omicron
```{r}
pre_omicron <- covid_data_simulation_matched %>% filter(cov_grp==0)

covs <- pre_omicron %>% 
  select(encAge,gender,raceEthnicity,dischargeLocation2,encDeathDerived,
         dischargeDispositionGroup2,prevDischarge90Days,LOS,facility_admission,
         starts_with("elix_"),
         maxTemp,medRR,medSBP,medDBP,maxALT,maxTBILI,minALB,minSODIUM,maxCREAT,
         minPLT,maxWBC,minHCT,maxGLU,ICUalgo,serviceGroup2,ttmatch_days,matchtodischarge_days,
         covVaxEver,covVaxLast4months,covVaxCumSum)

bal.tab(case ~ covs, data = pre_omicron, binary = "std", continuous = "std")
```

### Omicron
```{r}
post_omicron <- covid_data_simulation_matched %>% filter(cov_grp==1)

covs <- post_omicron  %>% 
  select(encAge,gender,raceEthnicity,dischargeLocation2,encDeathDerived,
         dischargeDispositionGroup2,prevDischarge90Days,LOS,facility_admission,
         starts_with("elix_"),
         maxTemp,medRR,medSBP,medDBP,maxALT,maxTBILI,minALB,minSODIUM,maxCREAT,
         minPLT,maxWBC,minHCT,maxGLU,ICUalgo,serviceGroup2,ttmatch_days,matchtodischarge_days,
         covVaxEver,covVaxLast4months,covVaxCumSum)

bal.tab(case ~ covs, data = post_omicron, binary = "std", continuous = "std")
```


## Outcomes
```{r,include=FALSE}
# make a copy of matched data 
covid_data_simulation_matched2 <- covid_data_simulation_matched %>% 
  group_by(matches) %>% 
  mutate(hospitalDay_normalized = hospitalDay-min(hospitalDay), 
         hospitalDay0_normalized = hospitalDay0-min(hospitalDay),
         sex_male = if_else(gender=="Male",1,0))

nrow(distinct(covid_data_simulation_matched2,matchid))
nrow(distinct(covid_data_simulation_matched2,matches))
```


```{r}
##############
#UPDATED: Tom#
coefSmry.lm <- function(in_testcoef,tp,eventLBL){
  
  if (tp=="pre-omicron"){
    out <- data.frame(event=eventLBL,
                      po_estimate=in_testcoef[2,1], 
                      po_conf_low=in_testcoef[2,5],
                      po_conf_high=in_testcoef[2,6],
                      po_pvalue= in_testcoef[2,4],
                      metric = "Difference")
} else {
    out <- data.frame(event=eventLBL,
                      o_estimate=in_testcoef[2,1], 
                      o_conf_low=in_testcoef[2,5],
                      o_conf_high=in_testcoef[2,6],
                      o_pvalue= in_testcoef[2,4],
                      metric = "Difference")
}
  return(out)
}

# 5/8/2024 Adding new function for median differences
coefSmry.lm.med <- function(in_testcoef,tp,eventLBL){
  
  if (tp=="pre-omicron"){
    out <- data.frame(event=eventLBL,
                      po_estimate=in_testcoef[2,1], 
                      po_conf_low=in_testcoef[2,5],
                      po_conf_high=in_testcoef[2,6],
                      po_pvalue= in_testcoef[2,4],
                      metric = "Difference")
} else {
    out <- data.frame(event=eventLBL,
                      o_estimate=in_testcoef[2,1], 
                      o_conf_low=in_testcoef[2,5],
                      o_conf_high=in_testcoef[2,6],
                      o_pvalue= in_testcoef[2,4],
                      metric = "Difference")
}
  return(out)
}

##############

##############
#UPDATED: Tom#
coefSmry.glmbinomial <- function(in_testcoef,tp,eventLBL){
  
  if (tp=="pre-omicron"){
    out <- data.frame(event=eventLBL,
                      po_estimate=exp(in_testcoef[2,1]), 
                      po_conf_low=exp(in_testcoef[2,5]),
                      po_conf_high=exp(in_testcoef[2,6]),
                      po_pvalue= in_testcoef[2,4],
                      metric = "Relative Risk")
  } else {
    out <- data.frame(event=eventLBL,
                      o_estimate=exp(in_testcoef[2,1]), 
                      o_conf_low=exp(in_testcoef[2,5]),
                      o_conf_high=exp(in_testcoef[2,6]),
                      o_pvalue= in_testcoef[2,4],
                      metric = "Relative Risk")
  }
  return(out)
}


##############

##############
#UPDATED: Tom#
coefSmry_cox <- function(fit,tp,eventLBL){
  
  out <- fit %>%  
  tidy(conf.int = TRUE, exponentiate = TRUE) %>% 
  select(estimate, starts_with("conf"),p.value)
  
  out <- out %>% mutate(event=eventLBL, metric = "Hazard ratio")
  
  if (tp=="pre-omicron"){
    out <- out %>% 
      rename(po_estimate=estimate,po_conf_low=conf.low,po_conf_high=conf.high,po_pvalue=p.value)
} else {
    out <- out %>% 
      rename(o_estimate=estimate,o_conf_low=conf.low,o_conf_high=conf.high,o_pvalue=p.value)
}
  
  return(out)
}
##############

pre_omicron <- covid_data_simulation_matched2 %>% filter(cov_grp==0)
post_omicron <- covid_data_simulation_matched2 %>% filter(cov_grp==1)

```

### Adjusted RR Function ###
```{r}
adjRR <- function(indata,omicrongrp,outcome,coefs,dsc) {
  
   if (omicrongrp=="pre-omicron"){
    dsn <- indata %>% filter(cov_grp==0)
  } else {
    dsn <- indata %>% filter(cov_grp==1)
  }
  
  
  f <- as.formula(
  paste(outcome, 
        paste(coefs, collapse = " + "), 
        sep = " ~ "))
  
  mod = glm(f,
            data =dsn, family = poisson(link = "log"))
  
  fit <- cbind(coeftest(mod, vcov = vcovHC(mod, type = "HC0")), coefci(mod, vcov = vcovHC(mod, type = "HC0"), level = 0.95))
  
  adjRRout = coefSmry.glmbinomial(fit,omicrongrp,paste0(dsc," (Relative Risk)"))
}
```

### Adjusted RR Function ###
```{r}
# Define coefficient sets
cov1 <- c("case","maxO2device_none","maxO2device_nc")
cov2 <- c("case","maxO2device_none","maxO2device_nc","covVaxEver","covVaxLast4months","covVaxCumSum","maxTemp","maxALT")
cov3 <- c("case","maxO2device_none","maxO2device_nc","covVaxEver","covVaxLast4months","covVaxCumSum","maxTemp","maxALT",
          "elix_DIAB","elix_RENLFL","ccsr_cat_prefix_INF","ccsr_cat_prefix_INJ","ccsr_cat_prefix_RSP","minSODIUM","minPLT","maxWBC")
cov4 <- c("case","covVaxCumSum")
```

### New admission to ICU After Match Day (RR) ###
```{r}
new_events_icu <- covid_data_simulation_matched %>% 
  rename(event_flg=after_match_new_icu)

new_icu_RR <- adjRR(new_events_icu,"pre-omicron","event_flg",cov1,"New admission to ICU After Match Day")

new_icu_RR2 <- adjRR(new_events_icu,"pre-omicron","event_flg",cov2,"New admission to ICU After Match Day")

new_icu_RR3 <- adjRR(new_events_icu,"pre-omicron","event_flg",cov3,"New admission to ICU After Match Day")

new_icu_RR4 <- adjRR(new_events_icu,"omicron","event_flg",cov4,"New admission to ICU After Match Day")
```


### New Need for High Flow O2 After Match Day (RR) ###
```{r}

new_events_HF <- covid_data_simulation_matched %>% 
  rename(event_flg=after_match_new_hf)

new_hf_RR <- adjRR(new_events_HF,"pre-omicron","event_flg",cov1,"New Need for High Flow O2 After Match Day")

new_hf_RR2 <- adjRR(new_events_HF,"pre-omicron","event_flg",cov2,"New Need for High Flow O2 After Match Day")

new_hf_RR3 <- adjRR(new_events_HF,"pre-omicron","event_flg",cov3,"New Need for High Flow O2 After Match Day")

new_hf_RR4 <- adjRR(new_events_HF,"omicron","event_flg",cov4,"New Need for High Flow O2 After Match Day")
```



### New Need for BIPAP After Match Day (RR) ###
```{r}
new_events_BIPAP <- covid_data_simulation_matched %>% 
  rename(event_flg=after_match_new_bipap)
  
new_bipap_RR <- adjRR(new_events_BIPAP,"pre-omicron","event_flg",cov1,"New Need for BIPAP After Match Day")

new_bipap_RR2 <- adjRR(new_events_BIPAP,"pre-omicron","event_flg",cov2,"New Need for BIPAP After Match Day")

new_bipap_RR3 <- adjRR(new_events_BIPAP,"pre-omicron","event_flg",cov3,"New Need for BIPAP After Match Day")

new_bipap_RR4 <- adjRR(new_events_BIPAP,"omicron","event_flg",cov4,"New Need for BIPAP After Match Day")
```



### New Need for Mechanical Ventilation After Match Day (RR) ###
```{r}
new_events_VENT <- covid_data_simulation_matched %>% 
  rename(event_flg=after_match_new_vent)

new_vent_RR <- adjRR(new_events_VENT,"pre-omicron","event_flg",cov1,"New Need for Mechanical Ventilation After Match Day Match Day")

new_vent_RR2 <- adjRR(new_events_VENT,"pre-omicron","event_flg",cov2,"New Need for Mechanical Ventilation After Match Day Match Day")

new_vent_RR3 <- adjRR(new_events_VENT,"pre-omicron","event_flg",cov3,"New Need for Mechanical Ventilation After Match Day Match Day")

new_vent_RR4 <- adjRR(new_events_VENT,"omicron","event_flg",cov4,"New Need for Mechanical Ventilation After Match Day Match Day")
```


### New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day (RR) ###
```{r}
new_events_O2 <- covid_data_simulation_matched %>% 
  rename(event_flg=after_match_new_hfbipapvent)

new_o2_RR <- adjRR(new_events_O2,"pre-omicron","event_flg",cov1,"New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day")

new_o2_RR2 <- adjRR(new_events_O2,"pre-omicron","event_flg",cov2,"New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day")

new_o2_RR3 <- adjRR(new_events_O2,"pre-omicron","event_flg",cov3,"New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day")

new_o2_RR4 <- adjRR(new_events_O2,"omicron","event_flg",cov4,"New Need for High Flow O2, BIPAP, Or Mechanical Ventilation After Match Day")
```

### Difference Function ###
```{r}
difference <- function(dsn,omicrongrp,type,outcome,coefs,dsc) {
  
  # Pre-Omicron
  f <- as.formula(
    paste(outcome,
          paste(coefs, collapse = " + "),
          sep = " ~ "))
  
  mydata = dsn
  
  if (type=="meandiff"){
    
    M <- lm(f, data = dsn)
  
    testcoef = cbind(coeftest(M, vcov = vcovCL, cluster = ~matchid),coefci(M, vcov = vcovCL, cluster = ~matchid))
    testcoef
  
    ##############
    #UPDATED: Tom#
    md_po <-coefSmry.lm(testcoef,omicrongrp,dsc)
    ##############
  }else {
    
    M <- rq(f, data = mydata)
    myboot = boot.rq(model.matrix(f, data = mydata), model.frame(f, data = mydata)[,1], R = 1e4)
    myconfint = t(apply(myboot$B, 2, quantile, c(0.025,0.975)))
    testcoef = cbind(summary(M, se = "ker")$coef, myconfint)
    
    md_po <- coefSmry.lm.med(testcoef,omicrongrp,paste0(dsc," Median Difference"))
  }
  

  

}
```

```{r}
### Days from Match Day to Discharge ###
covid_data_simulation_matched3 <- pre_omicron %>% 
    mutate(match_to_discharge_days= as.numeric(dischargeDT-date)+1)

mtd = difference(covid_data_simulation_matched3,"pre-omicron", "meandiff","match_to_discharge_days",cov1,"Days from Match Day to Discharge")

mtd_med = difference(covid_data_simulation_matched3,"pre-omicron", "mediandiff","match_to_discharge_days",cov1,"Days from Match Day to Discharge")

mtd2 = difference(covid_data_simulation_matched3,"pre-omicron", "meandiff","match_to_discharge_days",cov2,"Days from Match Day to Discharge")

mtd_med2 = difference(covid_data_simulation_matched3,"pre-omicron", "mediandiff","match_to_discharge_days",cov2,"Days from Match Day to Discharge")

mtd3 = difference(covid_data_simulation_matched3,"pre-omicron", "meandiff","match_to_discharge_days",cov3,"Days from Match Day to Discharge")

mtd_med3 = difference(covid_data_simulation_matched3,"pre-omicron", "mediandiff","match_to_discharge_days",cov3,"Days from Match Day to Discharge")

covid_data_simulation_matched3 <- post_omicron %>% 
    mutate(match_to_discharge_days= as.numeric(dischargeDT-date)+1)

mtd4 = difference(covid_data_simulation_matched3,"omicron", "meandiff","match_to_discharge_days",cov4,"Days from Match Day to Discharge")

mtd_med4 = difference(covid_data_simulation_matched3,"omicron", "mediandiff","match_to_discharge_days",cov4,"Days from Match Day to Discharge")
```

### Hospital Length of Stay ###
```{r}
los = difference(pre_omicron,"pre-omicron", "meandiff","LOS",cov1,"Hospital Length of Stay")

los_med = difference(pre_omicron,"pre-omicron", "mediandiff","LOS",cov1,"Hospital Length of Stay")

los2 = difference(pre_omicron,"pre-omicron", "meandiff","LOS",cov2,"Hospital Length of Stay")

los_med2 = difference(pre_omicron,"pre-omicron", "mediandiff","LOS",cov2,"Hospital Length of Stay")

los3 = difference(pre_omicron,"pre-omicron", "meandiff","LOS",cov3,"Hospital Length of Stay")

los_med3 = difference(pre_omicron,"pre-omicron", "mediandiff","LOS",cov3,"Hospital Length of Stay")

los4 = difference(post_omicron,"omicron", "meandiff","LOS",cov4,"Hospital Length of Stay")

los_med4 = difference(post_omicron,"omicron", "mediandiff","LOS",cov4,"Hospital Length of Stay")
```


### Hospital Length of Stay (Survivors Only) ###
```{r}
# Pre-Omicron
pre_omicron_surv <- pre_omicron %>% filter(encDeathDerived==0)

los_survivors = difference(pre_omicron_surv,"pre-omicron", "meandiff","LOS",cov1,"Hospital Length of Stay (Survivors Only)")

los_survivors_med = difference(pre_omicron_surv,"pre-omicron", "mediandiff","LOS",cov1,"Hospital Length of Stay (Survivors Only)")

los_survivors2 = difference(pre_omicron_surv,"pre-omicron", "meandiff","LOS",cov2,"Hospital Length of Stay (Survivors Only)")

los_survivors_med2 = difference(pre_omicron_surv,"pre-omicron", "mediandiff","LOS",cov2,"Hospital Length of Stay (Survivors Only)")

los_survivors3 = difference(pre_omicron_surv,"pre-omicron", "meandiff","LOS",cov3,"Hospital Length of Stay (Survivors Only)")

los_survivors_med3 = difference(pre_omicron_surv,"pre-omicron", "mediandiff","LOS",cov3,"Hospital Length of Stay (Survivors Only)")

post_omicron_surv <- post_omicron %>% filter(encDeathDerived==0)

los_survivors4 = difference(post_omicron_surv,"omicron", "meandiff","LOS",cov4,"Hospital Length of Stay (Survivors Only)")

los_survivors_med4 = difference(post_omicron_surv,"omicron", "mediandiff","LOS",cov4,"Hospital Length of Stay (Survivors Only)")
```



### Discharge to Home (RR) ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==0)

dc_home_RR <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_home",cov1,"Discharge to Home")

dc_home_RR2 <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_home",cov2,"Discharge to Home")

dc_home_RR3 <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_home",cov3,"Discharge to Home")

dc_home_RR4 <- adjRR(post_omicron,"omicron","discharge_home",cov4,"Discharge to Home")
```


### Discharge to Rehab (RR) ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==0)

dc_rehab_RR <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_rehab",cov1,"Discharge to Rehab")

dc_rehab_RR2 <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_rehab",cov2,"Discharge to Rehab")

dc_rehab_RR3 <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_rehab",cov3,"Discharge to Rehab")

dc_rehab_RR4 <- adjRR(post_omicron,"omicron","discharge_rehab",cov4,"Discharge to Rehab")
```


### Discharge to SNF (RR) ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==0)

dc_snf_RR <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_snf",cov1,"Discharge to SNF")

dc_snf_RR2 <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_snf",cov2,"Discharge to SNF")

dc_snf_RR3 <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_snf",cov3,"Discharge to SNF")

dc_snf_RR4 <- adjRR(post_omicron,"omicron","discharge_snf",cov4,"Discharge to SNF")
```


### Discharge to Hospice (RR) ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==0)

dc_hospice_RR <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_hospice",cov1,"Discharge to Hospice")

dc_hospice_RR2 <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_hospice",cov2,"Discharge to Hospice")

dc_hospice_RR3 <- adjRR(covid_data_simulation_matched3,"pre-omicron","discharge_hospice",cov3,"Discharge to Hospice")

dc_hospice_RR4 <- adjRR(post_omicron,"omicron","discharge_hospice",cov4,"Discharge to Hospice")
```

### Subdistributional Hazard Function ###
```{r}
subdisthazard <- function(dsn,omicrongrp,coefs,dsc) {
  
  outcome <- "Surv(LOS, dd2)"
  
  f <- as.formula(
    paste(outcome,
          paste(coefs, collapse = " + "),
          sep = " ~ "))
  
  # Code does not work when using etype
  # It looks like the default for finegray is to use the first value
  subdistdat = finegray(f, 
                        data=dsn)
  
  outcome <- "Surv(fgstart, fgstop, fgstatus)"
  
  f <- as.formula(
    paste(outcome,
          paste(coefs, collapse = " + "),
          sep = " ~ "))
  
  fgfit <- coxph(f,
                 weight=fgwt, data=subdistdat)
  
  sh <- coefSmry_cox(fgfit,omicrongrp,paste0(dsc," - Subdistributional Hazard")) %>% 
    # row 1 is for case; every coefficient will have a row, only want to report case
    filter(row_number()==1)
  
  return(sh)
}
```

### Discharge to Hospice - Subdistributional Hazard ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
  mutate(
    dd2 = case_when(
      dischargeDispositionGroup2=="Hospice" ~ 1,
      dischargeDispositionGroup2=="Rehabilitation facility" ~ 2,
      dischargeDispositionGroup2=="Skilled nursing facility" ~ 3,
      dischargeDispositionGroup2=="Other" ~ 4,
      dischargeDispositionGroup2=="Death" ~ 5,
      dischargeDispositionGroup2=="Home" ~ 6,
      ),
    dd2 = factor(dd2, levels = c(0,1,2,3,4,5,6),
                              labels = c("Nothing","Hospice","Rehabilitation facility","Skilled nursing facility","Other","Death","Home")))
  
str(covid_data_simulation_matched3$dd2)
  
covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)
  
  
# Pre-Omicron
po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)
  
 
hospice_sh <- subdisthazard(po,"pre-omicron",cov1,"Discharge to Hospice")

hospice_sh2 <- subdisthazard(po,"pre-omicron",cov2,"Discharge to Hospice")

hospice_sh3 <- subdisthazard(po,"pre-omicron",cov3,"Discharge to Hospice")

o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

hospice_sh4 <- subdisthazard(o,"omicron",cov4,"Discharge to Hospice")
```


### Discharge to Hospice or Death - Subdistributional Hazard ###
```{r}

  covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
    mutate(
           dd2 = case_when(
             encDeathDerived==1 | dischargeDispositionGroup2=="Death" | dischargeDispositionGroup2=="Hospice" ~ 1,
             dischargeDispositionGroup2=="Rehabilitation facility" ~ 2,
             dischargeDispositionGroup2=="Skilled nursing facility" ~ 3,
             dischargeDispositionGroup2=="Other" ~ 4,
             dischargeDispositionGroup2== "Home" ~ 5,
           ),
           
           dd2 = factor(dd2, levels = c(0,1,2,3,4,5),
                              labels = c("Nothing","Death/Hospice","Rehabilitation facility","Skilled nursing facility","Other","Home")))
  
  str(covid_data_simulation_matched3$dd2)
  
  covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)
  
  # Pre-Omicron
  po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)
  

deathhospice_sh <- subdisthazard(po,"pre-omicron",cov1,"Discharge to Hospice or Death")

deathhospice_sh2 <- subdisthazard(po,"pre-omicron",cov2,"Discharge to Hospice or Death")

deathhospice_sh3 <- subdisthazard(po,"pre-omicron",cov3,"Discharge to Hospice or Death")

o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

deathhospice_sh4 <- subdisthazard(o,"omicron",cov4,"Discharge to Hospice or Death")
```


### Discharged Alive (Home, SNF, Rehab, Hospice, Other) - Subdistributional Hazard ###
```{r}

  covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
    mutate(
           dd2 = case_when(
             dischargeDispositionGroup2=="Home" | dischargeDispositionGroup2=="Hospice" | dischargeDispositionGroup2=="Rehabilitation facility" | dischargeDispositionGroup2=="Skilled nursing facility" | dischargeDispositionGroup2=="Other" ~ 1,
             dischargeDispositionGroup2=="Death" ~ 2
           ),
           
           dd2 = factor(dd2, levels = c(0,1,2),
                              labels = c("Nothing","Discharged Alive","Death")))
  
  str(covid_data_simulation_matched3$dd2)
  
  covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)
  
  # Pre-Omicron
  po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)
  
 
dcalive_sh <- subdisthazard(po,"pre-omicron",cov1,"Discharged Alive (Home, SNF, Rehab, Hospice, Other)")

dcalive_sh2 <- subdisthazard(po,"pre-omicron",cov2,"Discharged Alive (Home, SNF, Rehab, Hospice, Other)")

dcalive_sh3 <- subdisthazard(po,"pre-omicron",cov3,"Discharged Alive (Home, SNF, Rehab, Hospice, Other)")


o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

dcalive_sh4 <- subdisthazard(o,"omicron",cov4,"Discharged Alive (Home, SNF, Rehab, Hospice, Other)")
```

### Discharged Alive (Home, SNF, Rehab, Other) - Subdistributional Hazard ###
```{r}

  covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
    mutate(
           dd2 = case_when(
             dischargeDispositionGroup2=="Home" | dischargeDispositionGroup2=="Rehabilitation facility" | dischargeDispositionGroup2=="Skilled nursing facility" | dischargeDispositionGroup2=="Other" ~ 1,
             dischargeDispositionGroup2=="Death" ~ 2,
             dischargeDispositionGroup2=="Hospice" ~ 3
           ),
           
           dd2 = factor(dd2, levels = c(0,1,2,3),
                              labels = c("Nothing","Discharged Alive","Death","Hospice")))
  
  str(covid_data_simulation_matched3$dd2)
  
  covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)
  
  # Pre-Omicron
  po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)
  
  

dcalive2_sh <- subdisthazard(po,"pre-omicron",cov1,"Discharged Alive (Home, SNF, Rehab, Other)")

dcalive2_sh2 <- subdisthazard(po,"pre-omicron",cov2,"Discharged Alive (Home, SNF, Rehab, Other)")

dcalive2_sh3 <- subdisthazard(po,"pre-omicron",cov3,"Discharged Alive (Home, SNF, Rehab, Other)")

o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

dcalive2_sh4 <- subdisthazard(o,"omicron",cov4,"Discharged Alive (Home, SNF, Rehab, Other)")
```

### Discharged To Facility (SNF, Rehab, Hospice) - Subdistributional Hazard ###
```{r}
  covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
    mutate(
           dd2 = case_when(
              dischargeDispositionGroup2=="Rehabilitation facility" | dischargeDispositionGroup2=="Skilled nursing facility" | dischargeDispositionGroup2=="Hospice" ~ 1,
             dischargeDispositionGroup2=="Death" ~ 2,
             dischargeDispositionGroup2=="Home"  ~ 3,
             dischargeDispositionGroup2=="Other" ~ 4
           ),
           
           dd2 = factor(dd2, levels = c(0,1,2,3,4),
                              labels = c("Nothing","Facility","Death","Home","Other")))
  
  str(covid_data_simulation_matched3$dd2)
  
  covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)
  
  # Pre-Omicron
  po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)
  


dcfacility_sh <- subdisthazard(po,"pre-omicron",cov1,"Discharged To Facility (SNF, Rehab, Hospice)")

dcfacility_sh2 <- subdisthazard(po,"pre-omicron",cov2,"Discharged To Facility (SNF, Rehab, Hospice)")

dcfacility_sh3 <- subdisthazard(po,"pre-omicron",cov3,"Discharged To Facility (SNF, Rehab, Hospice)")

o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

dcfacility_sh4 <- subdisthazard(o,"omicron",cov4,"Discharged To Facility (SNF, Rehab, Hospice)")
```


### Hospital Death - Subdistributional Hazard ###
```{r}

  covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% 
    mutate(dd2 = case_when(
             encDeathDerived==1 | dischargeDispositionGroup2=="Death" ~ 1,
             dischargeDispositionGroup2== "Home" ~ 2,
             dischargeDispositionGroup2=="Rehabilitation facility" ~ 3,
             dischargeDispositionGroup2=="Skilled nursing facility" ~ 4,
             dischargeDispositionGroup2=="Other" ~ 5,
             dischargeDispositionGroup2=="Hospice" ~ 6
           ),
           
           dd2 = factor(dd2, levels = c(0,1,2,3,4,5,6),
                              labels = c("Nothing","Death","Home","Rehabilitation facility","Skilled nursing facility","Other","Hospice")))
  
  str(covid_data_simulation_matched3$dd2)
  
  covid_data_simulation_matched3 %>% ungroup() %>% select(dd2) %>% sapply(levels)
  
  
  # Pre-Omicron
  po <- covid_data_simulation_matched3 %>% filter(cov_grp==0)
  
 
hospdeath_sh <-subdisthazard(po,"pre-omicron",cov1,"Hospital Death")

hospdeath_sh2 <-subdisthazard(po,"pre-omicron",cov2,"Hospital Death")

hospdeath_sh3 <-subdisthazard(po,"pre-omicron",cov3,"Hospital Death")

o <- covid_data_simulation_matched3 %>% filter(cov_grp==1)

hospdeath_sh4 <-subdisthazard(o,"omicron",cov4,"Hospital Death")
```

### Hospital Death (RR) ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==0) %>%  
  mutate(dd2 = if_else(encDeathDerived==1 | dischargeDispositionGroup2=="Death", "Death",dischargeDispositionGroup2),
         hospital_death= if_else(dd2=="Death",1,0))

hospital_death_RR <- adjRR(covid_data_simulation_matched3,"pre-omicron","hospital_death",cov1,"Hospital Death")

hospital_death_RR2 <- adjRR(covid_data_simulation_matched3,"pre-omicron","hospital_death",cov2,"Hospital Death")

hospital_death_RR3 <- adjRR(covid_data_simulation_matched3,"pre-omicron","hospital_death",cov3,"Hospital Death")


covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==1) %>%  
  mutate(dd2 = if_else(encDeathDerived==1 | dischargeDispositionGroup2=="Death", "Death",dischargeDispositionGroup2),
         hospital_death= if_else(dd2=="Death",1,0))


hospital_death_RR4 <- adjRR(covid_data_simulation_matched3,"omicron","hospital_death",cov4,"Hospital Death")
```


### 30-day Mortality counting from match day (RR) ###
```{r}
max_admitDT <- max(covid_data_simulation$admitDT)

covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==0) %>% 
  # only look at hospitalization that could have data 30 days post discharge
  # filter(dischargeDT<=max_admitDT-30) %>% 
  mutate(deathDT_derived = date(deathDTS_derived),
         match_to_death_days = as.numeric((deathDT_derived - date) +1),
         death30day = if_else(!is.na(match_to_death_days) & match_to_death_days <= 30, 1, 0))

# N cases after filtering
nrow(covid_data_simulation_matched3 %>% filter(case==1))


death30day <- adjRR(covid_data_simulation_matched3,"pre-omicron","death30day",cov1,"30-day Mortality (counting from match day)")

death30day2 <- adjRR(covid_data_simulation_matched3,"pre-omicron","death30day",cov2,"30-day Mortality (counting from match day)")

death30day3 <- adjRR(covid_data_simulation_matched3,"pre-omicron","death30day",cov3,"30-day Mortality (counting from match day)")

covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==1) %>% 
  # only look at hospitalization that could have data 30 days post discharge
  # filter(dischargeDT<=max_admitDT-30) %>% 
  mutate(deathDT_derived = date(deathDTS_derived),
         match_to_death_days = as.numeric((deathDT_derived - date) +1),
         death30day = if_else(!is.na(match_to_death_days) & match_to_death_days <= 30, 1, 0))

death30day4 <- adjRR(covid_data_simulation_matched3,"omicron","death30day",cov4,"30-day Mortality (counting from match day)")
```


### 30-day Readmission counting from match day (RR) ###
```{r}
covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==0) %>%  
  # only look at hospitalization that could have data 30 days post discharge
  # filter(dischargeDT<=max_admitDT-30) %>% 
  mutate(nextAdmitDT = date(nextAdmitDTS),
         match_to_next_admit_days = as.numeric((nextAdmitDT - date)+1),
         readmit30day = if_else(!is.na(match_to_next_admit_days) & match_to_next_admit_days <= 30, 1, 0))

# N cases after filtering
print(nrow(covid_data_simulation_matched3 %>% filter(case==1)))

readmit30day <- adjRR(covid_data_simulation_matched3,"pre-omicron","readmit30day",cov1,"30-day Readmission (counting from match day)")

readmit30day2 <- adjRR(covid_data_simulation_matched3,"pre-omicron","readmit30day",cov2,"30-day Readmission (counting from match day)")

readmit30day3 <- adjRR(covid_data_simulation_matched3,"pre-omicron","readmit30day",cov3,"30-day Readmission (counting from match day)")

covid_data_simulation_matched3 <- covid_data_simulation_matched2 %>% filter(cov_grp==1) %>%  
  # only look at hospitalization that could have data 30 days post discharge
  # filter(dischargeDT<=max_admitDT-30) %>% 
  mutate(nextAdmitDT = date(nextAdmitDTS),
         match_to_next_admit_days = as.numeric((nextAdmitDT - date)+1),
         readmit30day = if_else(!is.na(match_to_next_admit_days) & match_to_next_admit_days <= 30, 1, 0))

readmit30day4 <- adjRR(covid_data_simulation_matched3,"omicron","readmit30day",cov4,"30-day Readmission (counting from match day)")
```

### 30d hospital-free days (counting from match day) ###
```{r}
hfd = difference(pre_omicron,"pre-omicron","meandiff","hospitalfree30day",cov1,"30d Hospital-Free Days")

hfd_med = difference(pre_omicron,"pre-omicron","mediandiff","hospitalfree30day",cov1,"30d Hospital-Free Days")

hfd2 = difference(pre_omicron,"pre-omicron","meandiff","hospitalfree30day",cov2,"30d Hospital-Free Days")

hfd_med2 = difference(pre_omicron,"pre-omicron","mediandiff","hospitalfree30day",cov2,"30d Hospital-Free Days")

hfd3 = difference(pre_omicron,"pre-omicron","meandiff","hospitalfree30day",cov3,"30d Hospital-Free Days")

hfd_med3 = difference(pre_omicron,"pre-omicron","mediandiff","hospitalfree30day",cov3,"30d Hospital-Free Days")

hfd4 = difference(post_omicron,"omicron","meandiff","hospitalfree30day",cov4,"30d Hospital-Free Days")

hfd_med4 = difference(post_omicron,"omicron","mediandiff","hospitalfree30day",cov4,"30d Hospital-Free Days")
```



### Outcome Summary ###
```{r}

# 4/20/24 adjusted subdistributional hazard ratios will report coefficients for all covariates. Only want values corresponding to case (first row)
os  <- bind_rows(new_icu_RR,new_hf_RR,new_bipap_RR,new_vent_RR,new_o2_RR,
                 mtd,mtd_med,los,los_med,los_survivors,los_survivors_med,
                 dc_home_RR,dc_rehab_RR,dc_snf_RR,dc_hospice_RR,hospice_sh,deathhospice_sh,
                   dcalive_sh,dcalive2_sh,dcfacility_sh,hospital_death_RR,hospdeath_sh,
                   death30day,readmit30day,hfd,hfd_med) %>% select(event,everything())

write.csv(os,file = file.path(outLoc,paste0("outcomes_",outfilesfx,"-1.csv")))


kable(os,
      digits = c(2,2, 2, 2,3,2, 2, 2,3),
      format.args = list(scientific = FALSE))

os2  <- bind_rows(new_icu_RR2,new_hf_RR2,new_bipap_RR2,new_vent_RR2,new_o2_RR2,
                 mtd2,mtd_med2,los2,los_med2,los_survivors2,los_survivors_med2,
                 dc_home_RR2,dc_rehab_RR2,dc_snf_RR2,dc_hospice_RR2,hospice_sh2,deathhospice_sh2,
                   dcalive_sh2,dcalive2_sh2,dcfacility_sh2,hospital_death_RR2,hospdeath_sh2,
                   death30day2,readmit30day2,hfd2,hfd_med2) %>% select(event,everything())

write.csv(os2,file = file.path(outLoc,paste0("outcomes_",outfilesfx,"-2.csv")))


kable(os2,
      digits = c(2,2, 2, 2,3,2, 2, 2,3),
      format.args = list(scientific = FALSE))

os3  <- bind_rows(new_icu_RR3,new_hf_RR3,new_bipap_RR3,new_vent_RR3,new_o2_RR3,
                 mtd3,mtd_med3,los3,los_med3,los_survivors3,los_survivors_med3,
                 dc_home_RR3,dc_rehab_RR3,dc_snf_RR3,dc_hospice_RR3,hospice_sh3,deathhospice_sh3,
                   dcalive_sh3,dcalive2_sh3,dcfacility_sh3,hospital_death_RR3,hospdeath_sh3,
                   death30day3,readmit30day3,hfd3,hfd_med3) %>% select(event,everything())

write.csv(os3,file = file.path(outLoc,paste0("outcomes_",outfilesfx,"-3.csv")))


kable(os3,
      digits = c(2,2, 2, 2,3,2, 2, 2,3),
      format.args = list(scientific = FALSE))

os4  <- bind_rows(new_icu_RR4,new_hf_RR4,new_bipap_RR4,new_vent_RR4,new_o2_RR4,
                 mtd4,mtd_med4,los4,los_med4,los_survivors4,los_survivors_med4,
                 dc_home_RR4,dc_rehab_RR4,dc_snf_RR4,dc_hospice_RR4,hospice_sh4,deathhospice_sh4,
                   dcalive_sh4,dcalive2_sh4,dcfacility_sh4,hospital_death_RR4,hospdeath_sh4,
                   death30day4,readmit30day4,hfd4,hfd_med4) %>% select(event,everything())

write.csv(os4,file = file.path(outLoc,paste0("outcomes_",outfilesfx,"-4.csv")))


kable(os4,
      digits = c(2,2, 2, 2,3,2, 2, 2,3),
      format.args = list(scientific = FALSE))

```

